Equations & R Code

### 2017-03-07 manuscript/coexistence-stability_ms.Rmd
adds CHPC acknowledgement

ACKNOWLEDGMENTS
---------------
The National Science Foundation provided funding for this work through a Postdoctoral Research Fellowship in Biology to ATT (DBI-1400370) and a CAREER award to PBA (DEB-1054040). \new{We thank four anonymous reviewers for providing detailed and thoughtful comments that greatly improved the paper.}

>>>>

ACKNOWLEDGMENTS
---------------
The National Science Foundation provided funding for this work through a Postdoctoral Research Fellowship in Biology to ATT (DBI-1400370) and a CAREER award to PBA (DEB-1054040). \new{The support and resources from the Center for High Performance Computing at the University of Utah are gratefully acknowledged.} \new{We thank four anonymous reviewers for providing detailed and thoughtful comments that greatly improved the paper.}
